### 2020-03-01 ChapterBackground/chapterBackground.tex
Updated: More in Streamed Gaming

\section{Consistency in Real-Time Physics}
%(and the lack of, due to the challenges faced). Mostly limited to dead-reckoning
%https://books.google.co.uk/books?hl=en&lr=&id=ujfOBQAAQBAJ&oi=fnd&pg=PA307&dq=Physics+networked+games&ots=OC5YWxmd25&sig=vcxatd9Wl0_SdxCAUZvmP6BWl7I&redir_esc=y#v=onepage&q=Physics%20networked%20games&f=false

@@

\section{Streamed Gaming}
%The main foreseeable application of AP is Streamed Gaming, with the use of large multiplayer worlds, that are persistent and scalable with dedicated and elastic physics nodes. Physics is no longer limited to what can be simulated on a single machine and co-located render nodes solves the issue of higher latencies between the render node and physics simulation, the main problem with the use of physics in online gaming.

@@

Streamed Gaming services currently available include \cite{NVidiaGameStream} and \cite{PSNOW}. NVIDIA GRID technology is targeted specifically at Streamed Gaming \cite{NVIDIACloud}.

@@

In streamed gaming, each game instance resides on a single server. There is no technology to balance the real-time requirements of the game across multiple servers. The core problem is that all gaming technology is built and designed for single console/PC install and the greatest bottleneck is the inability to share physics calculations across machines. The technique presented in this study, AP, is intended for use in streamed gaming. AP allows multiple servers to simulate physics, meaning physics simulations are no longer limited in size and complexity to that which can be achieved by only a single server. This allows for game streaming servers to make use of multiple physics servers, the numbers of which can grow and shrink as needed by the game and greatly increase the limit on size and complexity of physics within the game.

>>>>

\section{Consistency in Real-Time Physics} \label{ConsistencyRealTimePhysics}
%(and the lack of, due to the challenges faced). Mostly limited to dead-reckoning
%https://books.google.co.uk/books?hl=en&lr=&id=ujfOBQAAQBAJ&oi=fnd&pg=PA307&dq=Physics+networked+games&ots=OC5YWxmd25&sig=vcxatd9Wl0_SdxCAUZvmP6BWl7I&redir_esc=y#v=onepage&q=Physics%20networked%20games&f=false

@@

\section{Streamed Gaming}
%The main foreseeable application of AP is Streamed Gaming, with the use of large multiplayer worlds, that are persistent and scalable with dedicated and elastic physics nodes. Physics is no longer limited to what can be simulated on a single machine

@@

The first successful demonstration of game streaming was in 2001 by G-cluster, whom publicly demonstrated game streaming over WiFi to a PDA in 2001 and launched a game-on-demand service in 2004 \cite{2016SurveyOnCloudGaming}. In the late 2000s, more companies introduced game streaming platforms such as OnLive \cite{OnLive}, Gaikai, and GameNow \cite{GameNow}. Due to financial difficulty in 2012, OnLive sold their patents to Sony and Gaikai and in 2012, Gaikai was bought by PSNOW \cite{PSNOW}.
Streamed Gaming services currently available include NVidia Geforce Now \cite{NVidiaGameStream}, PSNOW \cite{PSNOW}, Google Stadia\cite{Stadia} and Microsoft xCloud\cite{xCloud}. NVIDIA GRID hardware technology is targeted specifically at Streamed Gaming \cite{NVIDIACloud}.

@@

In recent years, streamed gaming has become an active area of research, with many studies focusing on the effects of latency on the quality of service, e.g. \cite{shea2013cloud, chen2011measuring, jarschel2011evaluation, lee2012all, choy2012brewing, chen2013quality}. The challenges in streamed gaming that remain are both technical as well as economical \cite{2016SurveyOnCloudGaming}.

In streamed gaming, each game instance resides on a single server. There is no technology to balance the real-time requirements of the game across multiple servers. The core problem is that all gaming technology is built and designed for single console/PC install and the greatest bottleneck is the inability to share physics calculations across machines.

The technique presented in this study, AP, is intended for use in streamed gaming. This study aims to be preliminary research into the division of game engines into microservices, allowing streamed gaming to take better advantage of cloud infrastructure, such as through elastic scaling of resources as needed. 
%As discussed in \ref{ConsistencyRealTimePhysics}, high latency between client and server
%
% Real-time physics as a microservice, combined with renderer microservices (using co-located render nodes) solves the issue of high latencies between client rendering and the physics simulation hosted on the server, the main problem with the use of physics in online gaming.
AP allows multiple servers to simulate physics, meaning physics simulations are no longer limited in size and complexity to that which can be achieved by only a single server. This allows for game streaming servers to make use of multiple physics servers, the numbers of which can grow and shrink as needed by the game and greatly increase the limit on size and complexity of physics within the game.
